---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(sumcolumnmiss)
library(dplyr)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# Sumcolumnmiss

The goal of the sumcolumnmiss package is to count missing values for all columns by group

## Installation

You can install the development version of GroupCount from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/sumcolumnmiss", quiet = TRUE)

```


## Examples


This illustration calculates the count of missing values in the airquality dataset, organized by the "cyl" column.

```{r}
library(sumcolumnmiss)
count_all_missing_by_group(airquality, Month)
```

This instance produces identical results to the previous one, highlighting an alternative approach to calling the count_all_missing_by_group(): by piping the dataset directly into the function.
```{r}
airquality |> count_all_missing_by_group(Month) 
```

The ".groups" parameter, when specified, enables us to maintain the grouped structure of the output based on the grouping column. In the example below, observe the grouped tibble output, which contrasts with the ungrouped tibble results from the earlier examples.
```{r}
count_all_missing_by_group(airquality, Month, .groups = "keep")
```

